Index measures for oak decline severity using phenotypic descriptors

### 2019-12-15 manuscript/manuscript.Rmd
couple of additions to discussion

This plot highlights the inaccuracies in manual field classifications of decline status with several trees classified as healthy controls that, when compared quantitatively to other trees, are in fact
in a decline state. 
Most notably this has occurred in a number of trees at Attingham, Hatchlands and Winding Wood. 
Also notable from Figure 3 is the disparity between the relative health of the healthier trees across the sites. 
The two dimensional space provided by these phenotypic indexes, for measuring decline severity is shown in Figure 1. 
The healthier trees at sites such as Attingham and Hatchlands were found to be in a more declined state than those at sites such as Langdale and Chestnuts.
The phenotypic descriptors used to calculate these indexes are easily measurable in the field and require no specialist equipment. 
They allow sensitive comparisons to be made for the same tree between years as well as comparisons of trees between different locations, which could have great utility in long term forest health monitoring for both forestry management and research.

@@

>>>>

This plot highlights the inaccuracies in manual field classifications of decline status with several trees classified as healthy controls that, when compared quantitatively to other trees, are in fact
in a decline state. 
Most notably this has occurred in a number of trees at Attingham, Hatchlands and Winding Wood. 
Also notable from Figure 3 is the disparity between the relative health of the healthier trees across the sites. 
The two dimensional space provided by these phenotypic indexes, for measuring decline severity is shown in Figure 1. 
The healthier trees at sites such as Attingham and Hatchlands were found to be in a more declined state than those at sites such as Langdale and Chestnuts.
The phenotypic descriptors used to calculate these indexes are easily measurable in the field and require no specialist equipment. 
They allow sensitive comparisons to be made for the same tree between years as well as comparisons of trees between different locations.

@@

which could have great utility in long term forest health monitoring for both forestry management and research.
